---
title: "Day4Interactive"
format: html
editor: visual
---

## Functions

Make a function that doubles a value

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(10.13)

double_value(my_dollars = 10.13)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)

double_value(monthly_income)
```

Create a function that returns an awesome restaurant name given a cool animal and your favorite food.

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant("lemur", " sushi")
```

Given temperature in degrees Fahrenheit, write a function that converts it to Celsius.

```{r}

temp_convert <- function(fahrenheit) {
  celsius = fahrenheit - 32 * (5/9)
  print(celsius)
}

temp_convert(52)
```

Create a function that given inputs of age and hometown, returns ("I am \_\_ years old, and I'm from \_\_")

```{r}
intro_age_hometown <- function(age, hometown) {
  print(paste("I am", age, "years old, and I'm from", hometown))
}

intro_age_hometown(age = 25, hometown = "Bethlehem")
```

#### print statements and return statements

Print: "show me"

Return: "store this so I can use this later"
