---
title: "Day4Interactive"
format: html
editor: visual
---

## Functions

Make a function that doubles a value

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(10.13)

double_value(my_dollars = 10.13)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)

double_value(monthly_income)
```

Create a function that returns an awesome restaurant name given a cool animal and your favorite food.

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant("lemur", " sushi")
```

Given temperature in degrees Fahrenheit, write a function that converts it to Celsius.

```{r}

temp_convert <- function(fahrenheit) {
  celsius = fahrenheit - 32 * (5/9)
  print(celsius)
}

temp_convert(52)
```

Create a function that given inputs of age and hometown, returns ("I am \_\_ years old, and I'm from \_\_")

```{r}
intro_age_hometown <- function(age, hometown) {
  print(paste("I am", age, "years old, and I'm from", hometown))
}

intro_age_hometown(age = 25, hometown = "Bethlehem")
```

#### print statements and return statements

Print: "show me"

Return: "store this so I can use this later"

## Functions with Conditionals

```{r}
calc_animal_age <- function(species, age_human_yrs) {
  if (species == "dog") {
    age_human_yrs * 7
  } else if (species == "goat") {
    age_human_yrs * 4.7
  } else {
    print("please enter dog or goat")
  }
}
```

```{r}
calc_animal_age("dog", 7)

calc_animal_age("goat", 4)

calc_animal_age("whale", 4)
```

Write a function that, given temperature in kelvin, if a user selects "metric" to the scale then return degrees celsius, if they select "english" then return degrees in fahrenheit

```{r}

kelvin_conversion <- function(unit_conv, unit_kelvin) {
  if (unit_conv == "metric") {
    unit_kelvin - 273.15
  } else if (unit_conv == "english") {
    (unit_kelvin - 273.15) * (5/9) + 32
  }
}

kelvin_conversion("metric", 40)
```

K = C + 273.15, C = K - 273.15

F = (K − 273.15) × 1.8 + 32
